Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-22 paper/Draft.tex
NI Theory Plot Remains Debugging but Still updated figures. Null test is to be done tmr.

\subsubsection{Replicating  \cite{fuhrer2018intrinsic}}

>>>>

In Table \ref{NullTestTable}, I reproduce a number of commonly used tests of null hypothesis of FIRE replying on differnet specific implications discussed in the previous section. I first reproduce the results from two papers, \cite{mankiw2003disagreement} and \cite{fuhrer2018intrinsic} and then proceed to show the results with the additional restrictions from ucnertainty.

The first set of tests utilize the dynamics of forecast errors. First, the forecast error should be on average unbiased. The forecast error should converge to zero. Second, forecast errors of non-overlapping forecasting horizon are not serially correlated.  Third, forecast errors should not be predicted by any information available at the time of forecast, including the forecast itself and other variable that is in the agent's information content.

The second batch of tests focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \cite{nordhaus1987forecasting}. In particular, I follow the model specifications in \cite{fuhrer2018intrinsic}. According to FIRE, rational forecast revision only responds to newly realized shocks thus it cannot be predicted by past information. For the same reason, regression coefficient of forecast for $y_{t+h}$  at time $t+1$ on that at $t-1$ is exactly equal to $1$, implying one-to-one responses.  A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.

\begin{table}[]\label{NullTestTable}
	\caption{Test of Rationality and Efficicency}
	\begin{tabular}{lll}

		\hline 
		& SCE & SPF        \\
		\hline 
		                                  &                             &             \\
	\end{tabular}
\end{table}
